### 2024-07-30 conteudo/background/codeduplication.tex
add t3 split on big

\begin{itemize}
	\begin{item}
		\textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2:} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3:} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4:} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}

@@

To evaluate the code clone detection approaches against the datasets, the works compute metrics using 
the predictions made related to the instances of the dataset. There are four possible outcomes when an 
instance is predicted by a code clone detection approach, which are:

>>>>

\begin{itemize}
	\begin{item}
		\textbf{Type-1(T1):} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2(T2):} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3(T3):} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4(T4):} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}

@@

The BigCloneBench dataset does an additional split on the code clone duplications types for the Type-3,
where the dataset separated the Type-3 into three types, which are Weak Type-3 (WT3), Medium Type-3 (MT3), 
Strong Type-3 (ST3), with the WT3 being closer to the Type-4 and ST3 being closer to the Type-2 \citep{bigclonebench}.
Finally,  the BigCloneBench dataset unifies the WT3 with the T4, resulting in 6 possible outcomes of a code pair, 
which are Type-1, Type-2, Strong Type-3, Medium Type-3, Weak Type-3/Type-4, and not a duplication \citep{bigclonebench}.

To evaluate the code clone detection approaches against the datasets, the researchs compute metrics using 
the predictions made related to the instances of the dataset. There are four possible outcomes when an 
instance is predicted by a code clone detection approach, which are:
